\mythesistitle

### 2011-11-20 src/synopsis.tex
1) added all the lit i have 2) changed the acronyms of study groups. fiiine, i obliged. but it is STILL IN THE CODE. 3) updated picture to match changes
shit just got real

\def \LLL {{\em ``{\bf L}aughing with Kafka''}} %{Consider the {\bf
                                %L}obster} 
\def \GGG {{\em ``{\bf G}irl with Curious Hair''}} % {``{\bf G}od Bless You,
                                % Mr. Franzen''} 
\def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}} %{{\bf B}room
                                %of the System} 
\def \TTT {{\em ``{\bf T}his is Water''}} %{``{\bf T}ennis, Trigonometry,
                                %Tornadoes: A Midwestern  Boyhood''}
                                %%{{\bf T}he Pale King}

@@

Let $U$ and $\cF$ represent the set of students and the set of study
groups respectively and the integers $n$ and $m$ denote the total
number students and study groups respectively. In relation to this
example, these are defined as follows. Also given below is the study group
allocation to students. \tnote{use tables}
\tnote{use other font for elements of sets}
\begin{enumerate}[]
\item {$U = \{$Pa,$\; $Pi,$\; $Sn,$\; $Wo,$\; $Vi,$\; $Li,$\; $Ch,$\;
    $Sa,$\; $Fr,$\; $Sc,$\; $Lu$\}$}
\item $\cF = \{L, G, B, T\}$
 % \item ${R = \{g, h, i, j, k\}}$
  % \item ${B = \{a, b, e, g\}}$
  % \item ${O = \{c, b, d\}}$
  % \item ${G = \{e, f , g, i\}}$
\item $L = \{$ Ch,$\; $ Sa,$\; $ Fr,$\; $ Sc,$\; $ Lu $\}$
\item $G = \{$ Pa,$\; $ Pi,$\; $ Vi,$\; $ Ch $\}$
\item $B = \{$ Su,$\; $ Pi,$\; $ Wo $\}$
\item $T = \{$ Vi,$\; $ Li,$\; $ Ch,$\; $ Fr $\}$
\item $n = |U| = 11$, $m = |\cF| = 4$
\end{enumerate}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.5]{../img/2_infinite_loop.png}
  \caption{{\residenceblock} street map with study group routes
    allocated. Routes are color coded as follows: red for
    \textcolor{red}{\bf L} group, blue for \textcolor{blue}{\bf G}
    group, orange for \textcolor{YellowOrange}{\bf B} group, green for
    \textcolor{green}{\bf T} group}
  \label{fig:streetmappath}
\end{figure}

>>>>

% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``{\bf G}irl with Curious Hair''}} 
% \def \BBB {{\em ``{\bf B}rief Interviews with Hideous Men''}}
% \def \TTT {{\em ``Everything and More: A Compact His{\bf T}ory of Infinity''}} 
% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf G}} 
% \def \xBBB {{\bf B}}
% \def \xTTT {{\bf T}}

%{\bf L}aughing {\bf G}irl {\bf B}rief {\bf T}his

% \def \LLL {{\em ``{\bf L}aughing with Kafka''}} 
% \def \GGG {{\em ``Brief {\bf I}nterviews with Hideous Men''}} 
% \def \BBB {{\em ``Broom of the {\bf S}ystem''}}
% \def \TTT {{\em ``Everything and More: {\bf A} Compact History of Infinity''}}

% \def \xLLL {{\bf L}}
% \def \xGGG {{\bf I}} 
% \def \xBBB {{\bf S}}
% \def \xTTT {{\bf A}}

\def \LLL {{\em ``{\bf B}rief Interviews with Hideous Men''}} 
\def \GGG {{\em ``The String {\bf T}heory''}} 
\def \BBB {{\em ``[{\bf W}]Rhetoric and the Math Melodrama''}}
\def \TTT {{\em ``{\bf F}ate, Time, and Language: An Essay on Free Will''}}

\def \xLLL {{\bf B}}
\def \xGGG {{\bf T}} 
\def \xBBB {{\bf W}}
\def \xTTT {{\bf F}}

%{{\em ``Everything and More: A Compact History of In{\bf F}inity''}} 
% {{\em ``Broom of {\bf T}he System''}} % {Consider the Lobster}
% {{\em ``God Bless You, Mr. {\bf F}ranzen''}}
% {{\em ``{\bf L}aughing with Kafka''}} 
% {{\em ``{\bf G}irl with Curious Hair''}} 
% {{\em ``Consider the {\bf L}obster|}}
% {{\em ``{\bf G}od Bless You, Mr. Franzen''}}
% {{\em ``{\bf T}ennis, Trigonometry,
%                                Tornadoes: A Midwestern  Boyhood''}}
% {{\em ``{\bf T}his is Water''}} %
% {\em {{\bf T}he Pale King}}

@@

Let $U$ and $\cF$ represent the set of students and the set of study
groups respectively and the integers $n$ and $m$ denote the total
number students and study groups respectively. In relation to this
example, these are defined as follows. Also given below is the study group
allocation to students. \tnote{use tables}
\tnote{use other font for elements of sets}
\begin{enumerate}[]
\item {$U = \{$Pa,$\; $Pi,$\; $Sn,$\; $Wo,$\; $Vi,$\; $Li,$\; $Ch,$\;
    $Sa,$\; $Fr,$\; $Sc,$\; $Lu$\}$}
\item $\cF = \{\xLLL, \xGGG, \xBBB, \xTTT\}$
\item $\xLLL = \{$ Ch,$\; $ Sa,$\; $ Fr,$\; $ Sc,$\; $ Lu $\}$
\item $\xGGG = \{$ Pa,$\; $ Pi,$\; $ Vi,$\; $ Ch $\}$
\item $\xBBB = \{$ Su,$\; $ Pi,$\; $ Wo $\}$
\item $\xTTT = \{$ Vi,$\; $ Li,$\; $ Ch,$\; $ Fr $\}$
\item $n = |U| = 11$, $m = |\cF| = 4$
\end{enumerate}

@@

\begin{figure}[h]
  \centering
%  \includegraphics[scale=0.5]{../img/2_infinite_loop.png}
  \includegraphics[scale=0.5]{../img/2_infinite_loop_BTWF.png}
  \caption{{\residenceblock} street map with study group routes
    allocated. Routes are color coded as follows: red for
    \textcolor{red}{\xLLL} group, blue for \textcolor{blue}{\xGGG}
    group, orange for \textcolor{YellowOrange}{\xBBB} group, green for
    \textcolor{green}{\xTTT} group}
  \label{fig:streetmappath}
\end{figure}
